Adaptive Sequential Model Selection

### 2015-07-08 paper.tex
small changes

By contrast, the LASSO path does not in general add the variable with the largest $t$-statistic. In that case, we could use instead the {\em selective next-$\lambda$ test}, which uses test statistic
\begin{equation}
  U_k = \inf\{ \lambda:\; \hat\beta^\lambda \notin \beta(E_{k-1})\}.
\end{equation}
The next-$\lambda$ statistic is $\sF_k$-measurable if we use the LASSO to select variables, but not if we use forward-stepwise. \WFcomment{Relate this to spacings test. Is this essentially the ``generalized spacings test?''}

>>>>

By contrast, the LASSO path does not in general add the variable with the largest $t$-statistic. In that case, we could use instead the {\em selective next-$\lambda$ test}, which uses test statistic
\begin{equation}
  U_k = \inf\{ \lambda:\; \hat\beta^\lambda \notin \beta(E_{k-1})\}.
\end{equation}
Here $\beta(E_{k-1})$ is the support of the ever-active set $E_{k-1}$, so that $U_k$ is the next $\lambda$ at which a new predictor is added by the lasso.
\RTcomment{Will: we never define $\beta(E)$: have i said it right?}
The next-$\lambda$ statistic is $\sF_k$-measurable if we use the LASSO to select variables. \WFcomment{Relate this to spacings test. Is this essentially the ``generalized spacings test?''}
